### 2019-04-03 papers/journal/conclusion.tex
Updated conclusion

\noindent 
%
\todo{Copid just to create a template}In the experiments, we have demonstrated the power of SMT solvers and the
value of careful encoding of the problems into SMT queries. 
%
We manage to scale the tool upto the size that makes tool biologically relevant. However, there are many further search problems or extensions that are of interest. 
%
For example, are there any k-connected graphs that can not be annotated into a VTS? 
%
This problem induces a quantifier alternation in an encoding. Therefore, a simple call to SAT solver will not work. 
%
We are planning to use QBF(quantified Boolean
formulas) solvers or develop iterative search algorithm for such queries.
%
One may be interested in counting the number of graphs that satisfy a given
property. 
%
Exact counting of the graphs using SAT solvers may prove to be very
difficult. 
%
We are also planning to employ some methods for approximate counting
of solutions.

>>>>

\noindent 
%
\todo{Copid just to create a template}
We have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
%
Our results contain many predictions which can in
principle be tested through cell-biological experiments. 
%
However, our current knowledge of the actual vesicle transport graph of a cell is very poor: it is likely that there are many vesicle transport routes that are still uncharacterized. Even in those instances where vesicles are known to exist, the precise molecular drivers of their creation and fusion are often unknown.
%
Therefore, a direct verification of our predictions based on graph connectedness alone is not likely. 
%
However, more indirect predictions based on how SNAREs are regulated can be
explored. 
%
In this context, the Sec/MUNC proteins or SNARE longin domains are interesting
targets of study~\cite{van2010one,rossi2004longins}.

\todo{Copid just to create a template}In the experiments, we have demonstrated the power of SMT solvers and the
value of careful encoding of the problems into SMT queries. 
%
We manage to scale the tool upto the size that makes tool biologically relevant. However, there are many further search problems or extensions that are of interest. 
%
For example, are there any k-connected graphs that can not be annotated into a VTS? 
%
This problem induces a quantifier alternation in an encoding. Therefore, a simple call to SAT solver will not work. 
%
We are planning to use QBF(quantified Boolean
formulas) solvers or develop iterative search algorithm for such queries.
%
One may be interested in counting the number of graphs that satisfy a given
property. 
%
Exact counting of the graphs using SAT solvers may prove to be very
difficult. 
%
We are also planning to employ some methods for approximate counting
of solutions.
